### 2016-04-04 chapters/scenarios.tex
evaluation added to the scenario

The current version of \textit{Odoo} (version 9.0, released \mbox{October 1, 2015)} has 465~contributors and over 101.200~commits. They have developed 266 features which are all inside of a top hierarchy folder named "addons". Each of them contain code as well as a configuration file named "\textunderscore\textunderscore openerp\textunderscore\textunderscore.py". Inside this file there are all the relevant informations for this feature, like dependencies, summaries , categories, versions and more descriptive informations.

@@

@@

{\color{red}TODO: Auswertung}

>>>>

The current version of \textit{Odoo} (version 9.0, released \mbox{October 1, 2015)} has 465~contributors and over 101.200~commits. They have developed 266 features which are all inside of a top hierarchy folder named ``addons''. Each of them contain code as well as a configuration file named ``\_\_openerp\_\_.py''. Inside this file there are all the relevant informations for this feature, like dependencies, summaries , categories, versions and more descriptive informations. Inside the \textit{Odoo} repository there are also other directories, like ``doc'' for documentary files, ``setup'' for deployment scripts on various platforms and ``openerp'' with the core code. However, as the variability is only contained within the features, the only relevant directory for this work is ``addons''.

@@

The choices made by the user have to be evaluated. This happens after each single question got answered. Especially the validity needs to be ensured at every time. Optimally, the questionnaire gets designed in such a way, that it is impossible to create an invalid configuration by just answering it. However, as the questionnaire itself does not get checked for validity, checking the answers adds that needed reassurance for validity. To check for validity, the dependencies assigned to a selected answer are checked. If a dependency-feature is previously unselected (undefined), it get (de-) selected according to the definition in the questionnaire. But if is already is in a state of (de-) selection, that doesn't match the state assigned in the questionnaire, an error occurs and warns the user of an invalid configuration.

As stated in Section~\ref{ch:quest-impl}, it is possible to define a dynamic ordering of the questions within the questionnaire according to the given answer. The next step in evaluating the user input is looking for the correct question to be asked next. If there is a next question explicitly stated in the selected answer, that question gets displayed next. Else, if there are questions left unanswered in the questionnaire, that occur after the current questions, the question displayed next is the question following the current question in the definition. If there is no next question to be displayed, the questionnaire is considered finished. Optimally, this also results in a final configuration of a product. However, our design also allows for partial configurations as a result of an executed questionnaire. In the case of a finished configuration, this configuration gets passed to FeatureIDE, which then compiles the configured product.

@@
